---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SCFMonitor

<!-- badges: start -->
[![R-CMD-check](https://github.com/AzuleneG/SCFMonitor/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/AzuleneG/SCFMonitor/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/AzuleneG/SCFMonitor/branch/master/graph/badge.svg)](https://app.codecov.io/gh/AzuleneG/SCFMonitor?branch=master)
<!-- badges: end -->

The goal of SCFMonitor is to enable **Gaussian** the quantum chemistry calculation software users to easily read the Gaussian .log files and monitor the SCF convergence and geometry optimization process with little effort and clear, beautiful and clean outputs. It can generate graphs using tidyverse to let users check SCF convergence and geometry optimization process real time. The software supports processing .log files remotely using with `rbase::url()`. This software is a suitcase for saving time and energy for the researchers, supporting multiple versions of Gaussian.

## Installation

You can install the development version of SCFMonitor from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AzuleneG/SCFMonitor")
```

## Example

This is a basic example which shows how to monitor a SCF convergence process:

```{r example}
library(SCFMonitor)

# Generate the plots
MultipleRoundOptiSCFIntegratedMonitor(SCFMonitorExample())
OptiSCFConvergenceRoundMonitor(SCFMonitorExample())
OptiConvergenceMonitor(SCFMonitorExample())
```

When using with the real log files, please replace `SCFMonitorExample()` to the directory of the .log file. For example, `"~/GaussianJobs/opti/job.log"` or `"C:\GaussianJobs\opti\job.log"`

